This is an example of article title

### 2025-10-28 paper/paper.tex
A few final touhes/formulations for the Bezier example.

\section{An example how to use {\texttt{LieGroups.jl}}}%
\label{sec:Example}

@@

We evaluate the corresponding Bézier curves on both Lie groups using the code in~\ref{lst:bezierLieGroupExample}.
\begin{lstlisting}[
    language = Julia,
    numbers=left,
    label={lst:bezierLieGroupExample},
    caption={Evaluating Bézier curves on \(\mathrm{SE}(2)\) and \(\mathrm{SO}(2) \times \mathcal T(2)\).}
]
ts = range(0, 1, length=35)
q1 = [
    deCasteljauLieGroup(SO2xT2, cp, t) for t in ts
]
q2 = [deCasteljauLieGroup(SE2, cp, t) for t in ts]
\end{lstlisting}

@@

    \begin{tikzpicture}
        \begin{axis}[
            grid=major,
            width=.5\textwidth,
            legend style={at={(0.95,0.9)}},
            xmin=-0.05, xmax=1.05,
            ymin=-0.525, ymax=0.625,
            unit vector ratio=1 1,
            title style={yshift=-.5\baselineskip,},
            title={Two Bézier curves on different Lie groups},
        ]
            % Control points
            % Quiver plot from CSV file
            \addplot[
                quiver={u=\thisrow{u}, v=\thisrow{v}, scale arrows=\arrowscale},
                -stealth, very thick, TolMutedBlue,
            ] table[col sep=comma] {data/bezier_example_control_points.csv};
            \addlegendentry{Control points}
            % Plot the base points from CSV file
            \addplot[only marks, mark=*, mark size=2pt, TolMutedBlue, forget plot,
                ] table[col sep=comma] {data/bezier_example_control_points.csv};
            % SO2xR2 Curve and quiver
            \addplot[solid, thick, TolMutedSand, forget plot] table[col sep=comma, x=x, y=y] {data/bezier_example_so2r2_dense_curve.csv};
            % Quiver plot from CSV file
            \addplot[
                quiver={u=\thisrow{u}, v=\thisrow{v}, scale arrows=\arrowscale},
                -stealth, TolMutedSand,
            ] table[col sep=comma] {data/bezier_example_so2r2.csv};
            \addlegendentry{$\mathrm{SO}(2)\times \mathcal T(2)$}
            % Plot the base points from CSV file
            \addplot[only marks, mark=*, mark size=1.5pt, TolMutedSand, forget plot,
                ] table[col sep=comma] {data/bezier_example_so2r2.csv};
            % SE2 Curve and quiver
            \addplot[solid, thick, TolMutedTeal, forget plot] table[col sep=comma, x=x, y=y] {data/bezier_example_se2_dense_curve.csv};
            % Quiver plot from CSV file
            \addplot[
                quiver={u=\thisrow{u}, v=\thisrow{v}, scale arrows=\arrowscale},
                -stealth, TolMutedTeal,
            ] table[col sep=comma] {data/bezier_example_se2.csv};
            \addlegendentry{$\mathrm{SE}(2)$}
            % Plot the base points from CSV file
            \addplot[only marks, mark=*, mark size=1.5pt, TolMutedTeal, forget plot,
                ] table[col sep=comma] {data/bezier_example_se2.csv};
        \end{axis}
    \end{tikzpicture}
    \caption{Bézier curves on the Lie groups \(\mathrm{SE}(2)\) (teal) and \(\mathrm{SO}(2) \times \mathbb{R}^2\) (sand) based on the same control points
    $g_1,\ldots,g_4$ (blue).}
\end{figure}

@@

{\color{red}TODO: Provide code for de-Casteljau algorithm on Lie groups.}

>>>>

\section{Examples how to use {\texttt{LieGroups.jl}}}%
\label{sec:Example}

@@

We evaluate the corresponding Bézier curves on both Lie groups using the Code~\ref{lst:bezierLieGroupExample}.
\begin{lstlisting}[
    language = Julia,
    numbers=left,
    label={lst:bezierLieGroupExample},
    caption={Evaluating Bézier curves on \(\mathrm{SE}(2)\) and \(\mathrm{SO}(2) \times \mathcal T(2)\).},
    mathescape
]
SO2 = SpecialOrthogonalGroup(2)
R2 = TranslationGroup(2)
SO2xR2 = SO2 $\times$ R2
ts = range(0, 1, length=35)
q1 = [
    deCasteljauLieGroup(SO2xT2, cp, t) for t in ts
]
SE2 = SpecialEuclideanGroup(2)
q2 = [deCasteljauLieGroup(SE2, cp, t) for t in ts]
\end{lstlisting}

@@

    \begin{tikzpicture}
        \begin{axis}[
            grid=major,
            width=.5\textwidth,
            legend style={at={(0.95,0.9)}},
            xmin=-0.05, xmax=1.05,
            ymin=-0.525, ymax=0.625,
            unit vector ratio=1 1,
            title style={yshift=-.5\baselineskip,},
            title={Two Bézier curves on different Lie groups},
        ]
            % Control points
            % Quiver plot from CSV file
            \addplot[
                quiver={u=\thisrow{u}, v=\thisrow{v}, scale arrows=\arrowscale},
                -stealth, very thick, TolMutedBlue,
            ] table[col sep=comma] {data/bezier_example_control_points.csv};
            \addlegendentry{Control points}
            % Plot the base points from CSV file
            \addplot[only marks, mark=*, mark size=2pt, TolMutedBlue, forget plot,
                ] table[col sep=comma] {data/bezier_example_control_points.csv};
            % SO2xR2 Curve and quiver
            \addplot[solid, thick, TolMutedSand, forget plot] table[col sep=comma, x=x, y=y] {data/bezier_example_so2r2_dense_curve.csv};
            % Quiver plot from CSV file
            \addplot[
                quiver={u=\thisrow{u}, v=\thisrow{v}, scale arrows=\arrowscale},
                -stealth, TolMutedSand,
            ] table[col sep=comma] {data/bezier_example_so2r2.csv};
            \addlegendentry{$\mathrm{SO}(2)\times \mathcal T(2)$}
            % Plot the base points from CSV file
            \addplot[only marks, mark=*, mark size=1.5pt, TolMutedSand, forget plot,
                ] table[col sep=comma] {data/bezier_example_so2r2.csv};
            % SE2 Curve and quiver
            \addplot[solid, thick, TolMutedTeal, forget plot] table[col sep=comma, x=x, y=y] {data/bezier_example_se2_dense_curve.csv};
            % Quiver plot from CSV file
            \addplot[
                quiver={u=\thisrow{u}, v=\thisrow{v}, scale arrows=\arrowscale},
                -stealth, TolMutedTeal,
            ] table[col sep=comma] {data/bezier_example_se2.csv};
            \addlegendentry{$\mathrm{SE}(2)$}
            % Plot the base points from CSV file
            \addplot[only marks, mark=*, mark size=1.5pt, TolMutedTeal, forget plot,
                ] table[col sep=comma] {data/bezier_example_se2.csv};
        \end{axis}
    \end{tikzpicture}
    \caption{Bézier curves on the Lie groups \(\mathrm{SE}(2)\) (teal) and \(\mathrm{SO}(2) \times \mathbb{R}^2\) (sand) based on the same control points
    $g_1,\ldots,g_4$ (blue).}
    \label{fig:Bezier}
\end{figure}

The resulting Bézier curves on both Lie groups are shown in Figure~\ref{fig:Bezier}.
One can see that the product Lie group works the same as if one would have done that
separately component-wise, while the Bézier curve on \(\mathrm{SE}(2)\) behaves differently.

@@
